Galaxy Zoo: Morphological Classifications for 150,000 Galaxies in HST Legacy Imaging

### 2016-05-17 writeup/gz_hubble_data.tex
rearranged S2
closes #95

@@

The GZH project contains images drawn from a number of different dedicated
surveys and sample selection criteria. The majority of the data (as implied by
the project name) were taken directly from \hst{} Legacy Surveys, all of which
primarily used imaging from the Advanced Camera for Surveys (ACS). Results from
the individual surveys have been combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog
\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
Table~\ref{tbl:gzh_numbers}.

@@

@@

\subsection{Galaxy selection}

In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

Single-epoch images from SDSS Stripe~82 were selected using the same criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
single-depth images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

\subsection{Image creation}

@@

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masked procedure was effective in preserving the color balance for
galaxies, retaining the visibility of faint features, but reduced the color
contrast in the sky noise and greatly improved the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

\subsection{Images with simulated nuclear point sources}

GZH also included a set of images designed to measure the effect of active
galactic nuclei (AGN) on morphological classifications. Since galactic nuclei
can have bright, unresolved optical emission, AGN have the potential to mimic
or distort the identification of a bulge component. The presence of an AGN was
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN was assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host.

@@

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images. These images consist of the same galaxy as it would appear
over a variety of redshifts. The input images are from the SDSS
\citep{yor00,str02} and are processed using the \ferengi{} code \citep{bar08a}
to match the observational properties of the \hst{} surveys out to $z=1$. These
images were classified in the GZH interface using the same classification
scheme as the original \hst{} images.

\subsection{Generating images of artificially-redshifted galaxies}

The GZH classifications include 288 unique galaxies originally generated from
SDSS imaging and processed with the \ferengi{} code. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets (in $N_z = 4$ bins) in order to be optimized for different target
minimum redshifts in \hst{} imaging.

The final number of \ferengi{} images produced for each galaxy is ultimately a
function of galaxy's redshift (since the new images cannot be resampled at
better angular resolution than the original SDSS data), as well as the number
of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
images produced for GZH.

@@

The GZH catalog is corrected for classification bias only for the first
question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
{\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
question, the catalog provides the additional parameters $\tt debiased$, $\tt
lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
$\tt best = lower~limit$; if neither condition applies, then 
$\tt best = weighted$. Flags are also given for the three responses of Task 01 to identify clean samples of galaxies with high likelihoods of being smooth, featured, or an artifact.  These are set as $\tt smooth/featured/artifact\_flag=1$ if $\rm f_{smooth/features/artifact\_best}>0.8$. For a galaxy to be flagged as ``smooth'', an additional criterion of $\tt correction\_type =~$0, 1, or 2 is applied. This is to account for the uncertainty in distinguishing between genuine ellipticals and disks whose features have been washed out due to surface brightness and redshift effects, as described in Section~\ref{sec:debiasing}.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226 & 0   \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$   &0   \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$   &0   \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$   &0   \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800 &0   \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727 &0   \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496 &0   \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669 &0  \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548 &0   \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287 &0   \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 118,425~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrlllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-faded Hubble images\label{tbl:catalog_faded}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829 &0 \\
AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198 &0 \\
AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$   &0 \\
AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820 &0 \\
AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$   &0 \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recolored}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{7}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Zooniverse ID} & 
\colhead{Survey ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{flag} &
\colhead{}
}
\small
\startdata
AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775 &0   \\
AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063 &0   \\
AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$  &1    \\
AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796 &0   \\
AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$  &1    \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

>>>>

The GZH project contains images drawn from a number of different dedicated
surveys and sample selection criteria. The majority of the data (as implied by
the project name) were sourced directly from \hst{} Legacy Surveys, all of which
primarily used imaging from the Advanced Camera for Surveys (ACS). In addition
to \hst{} images, the project uses images from SDSS Stripe~82, as well as
simulated \hst{} images from multiple sources. Below we provide details on each
source of imaging and describe the creation process for images shown to classifiers. 
We also detail the sources of metadata for galaxies in the sample, such as 
photometry and redshifts.

@@

Image information from
the individual surveys have been combined into a single photometric and
morphological database, the Advanced Camera for Surveys General Catalog
\citep[ACS-GC;][]{gri12}. A summary of the key parameters is given in
Table~\ref{tbl:gzh_numbers}.

@@

%Selection of galaxies from these samples is described in Section \ref{ssec:galselect} below. 
In the ACS-GC \citep{gri12}, individual galaxies were identified using a
combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
GOODS-S (2-epoch), and GOODS-N (2-epoch) surveys, respectively. The full-depth 
GOODS images from both fields included galaxies with $m<26.8$. This yielded a total of
113,166~images (Table~\ref{tbl:gzh_numbers}).

Images from \hst{} legacy surveys were used to create multiple different color and grayscale 
images using different depths and filter combinations; these are described further in Section 
\ref{ssec:images}. Additionally, the use of a small set of \hst{} images to create simulated 
images of active galactic nucleus (AGN) host galaxies is described in Section \ref{ssec:sim_agn}.

@@

\subsection{The Sloan Digital Sky Survey}\label{ssec:sdss}

The project includes images from the Sloan Digital Sky Survey \citep[SDSS;][]{yor00,str02}, 
in particular those from Data Release 7 \citep{aba09}. A small number of images 
were used in the creation of simulated \hst{} images, described in Sections 
\ref{ssec:ferengi} and \ref{sec:debiasing} below; the majority of SDSS images used 
in GZH were from Stripe~82. The Stripe~82 samples in GZH include single-epoch 
and co-added images, intended to facilitate comparison of morphological 
classification with image depth.

%The creation of 51,861 images from these sources is described in Section \ref{ssec:galselect} below.
Single-epoch images from SDSS Stripe~82 were selected using the same criteria
from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
images used were three-color composites using the $g^\prime$, $r^\prime$, and
$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
Co-added images from Stripe~82 were selected from the union of galaxies with
co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
single-depth images and matched to a co-add source. This resulted in a total
set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
were dimmer than the initial magnitude cut of 17.77.

\subsection{Simulated \hst{} images}\label{ssec:simulatedimages}

To facilitate correction of classifications in the presence of known biasing effects, 
GZH includes two different samples of simulated \hst{} images: real \hst{} galaxy images 
(Section \ref{ssec:legacy_surveys}) with nuclear emission added to simulate AGN 
host galaxies, and lower-redshift galaxy images from SDSS (Section \ref{ssec:sdss}), 
artificially redshifted from $0.3 \leq z \leq 1$. Each is described separately below.

\subsubsection{Images with simulated nuclear point sources}\label{ssec:sim_agn}

As active galactic nuclei often have bright, unresolved optical emission, AGN have the 
potential to mimic or distort the identification of a bulge component. GZH thus includes 
a set of images designed to measure the effect of AGN on morphological classifications. 
The presence of an AGN was
simulated by modeling the point spread function (PSF) of the telescope and then
inserting a bright source near the center of a real galaxy. For each image, the
simulated AGN was assigned one of three colors -- either blue, red, or flat
(white) as seen in the color images -- and a range of brightnesses such that
$L_\mathrm{ratio} \equiv L_\mathrm{galaxy}/L_\mathrm{AGN}$ is in
$(0.2,1.0,2.0,5.0,10.0,50.0)$. Combining these parameters generated 15~images
with different simulated AGN for each host, in addition to the original galaxy image.

\subsubsection{Generating images of artificially-redshifted galaxies}\label{ssec:ferengi}

The dimming and resolution effects of redshift can significantly affect galaxy classifications 
derived from any method. To facilitate corrections due to redshift, we include a sample 
of 288 galaxies with at redshifts such that available SDSS imaging can be transformed 
to simulate \hst{} imaging out to $z = 1$. The selection spanned a
variety of galaxy morphologies (as selected by GZ2 classifications) and
$r^\prime$-band surface brightnesses, and also spanned the redshift range of
SDSS targets (in $N_z = 4$ bins) in order to optimize for different target
minimum redshifts in \hst{} imaging. We redshifted the galaxies and produced simulated
\hst{} imaging using the \ferengi{} code \citep{bar08a}.

The final number of \ferengi{} images produced for each galaxy is ultimately a
function of galaxy's redshift (since the new images cannot be resampled at
better angular resolution than the original SDSS data), as well as the number
of $e$ values selected. Table~\ref{tbl:ferengivalues} summarizes the redshifted
images produced for GZH. The use of these images to correct for redshift-dependent
classification bias is described in Section \ref{sec:debiasing}.

%\subsection{Galaxy selection}\label{ssec:galselect}
%
%In the ACS-GC \citep{gri12}, individual galaxies were identified using a
%combination of \sextractor{} \citep{ber96} and the galaxy-profile fitting
%framework \galapagos{} \citep{bar12}. GZH included all galaxies with $m<23.5$,
%where $m$ is in the \Iband, \zband, or \iband{} for the AEGIS + COSMOS, GEMS +
%GOODS-S, and GOODS-N surveys, respectively. This yielded a total of
%113,166~images (Table~\ref{tbl:gzh_numbers}).
%
%Single-epoch images from SDSS Stripe~82 were selected using the same criteria
%from \citet{wil13}, which required limits of \texttt{petroR90\_r}$ >
%3$\arcsec~(where \texttt{petroR90\_r} is the radius containing 90\% of the
%$r^\prime$ Petrosian flux) and a magnitude brighter than $m_r < 17.77$. The
%images used were three-color composites using the $g^\prime$, $r^\prime$, and
%$i^\prime$ filters \citep{nie04}. 21,522 galaxies in SDSS met these criteria.
%Co-added images from Stripe~82 were selected from the union of galaxies with
%co-added magnitudes brighter than $17.77$~mag, and the galaxies detected in the
%single-depth images and matched to a co-add source. This resulted in a total
%set of 30,339 images. Of the images in the co-added sample, 5144 (17~percent)
%were dimmer than the initial magnitude cut of 17.77.

\subsection{Image creation}\label{ssec:images}

@@

In some cases, we found that attempting to emphasize faint features in the
images resulted in the sky noise taking the appearance of brightly colored
speckles. This impaired the aesthetics of the images and might have been a
distraction to visual classification.  To counteract this, a soft-edged object
mask was applied to the color images and a desaturation operation performed.
This masked procedure was effective in preserving the color balance for
galaxies, retaining the visibility of faint features while reducing the color
contrast in the sky noise and greatly improving the appearance of the images.
This solution was applied to the coadded Stripe~82, COSMOS and 5-epoch GOODS
images.

In addition to the main \hst{} legacy imaging sample with colored images described
as above, GZH also includes samples of \hst{} galaxy images with different color
prescriptions. In particular, there are 2 sets of 3,927 images each, drawn from the
COSMOS sample; the first has a dramatically reduced color saturation, and the second
has reversed the colors so that the blue and red filters have exchanged places in the
RGB image. The `faded' galaxy set facilitates measuring of possible variations in
classification due to the presence or absence of color features. The reversed-color set
enables an alternative test of potential color biases in classifications.
% I guess this means we need to say somewhere later that we don't see an effect (we don't, right?).
% Would also be good to cite here where we have done similar things in the past...

The simulated AGN host galaxy color images (described in Section \ref{ssec:sim_agn})
were created using the same prescription as for the GOODS 2-epoch imaging. The
artificially redshifted color images (Section \ref{ssec:ferengi}) were created using the
same prescription as for the AEGIS images.
% Edmond should verify the AEGIS bit above.

\subsection{Galaxy sample labels}\label{ssec:sample_labels}

The full GZH sample is composed of 7 different galaxy sub-samples. Throughout this
paper and in the published catalogs they are referred to with the following labels:

%\ref{tbl:catalog_hst}
\item \texttt{main}: \hst{} imaging with RGB colors making use of all available filters with typical saturation and in correct order, as described in Section \ref{ssec:images}. This sample includes AEGIS, COSMOS, GEMS, and full-depth GOODS (North and South) images. (118,425 galaxies)

%\ref{tbl:catalog_faded}
\item \texttt{faded}: a subset of COSMOS images with very low color saturation. (3,927 galaxies)

%\ref{tbl:catalog_recolored}
\item \texttt{recolored}: a subset of COSMOS images with red and blue channels reversed. Note: this sub-sample uses the same galaxies as the \texttt{faded} sub-sample. (3,927 galaxies)

%\ref{tbl:catalog_goods_shallow}
\item \texttt{goods-shallow}: Images from GOODS-North and GOODS-South, with color from 2 filters and imaged at 2-epoch depth. (6,144 galaxies)

%\ref{tbl:stripe82_single}
\item \texttt{stripe-82-single}: Single-epoch images from SDSS Stripe~82. (21,522 galaxies)

%\ref{tbl:stripe82_coadd}
\item \texttt{stripe-82-coadd}: Co-added images from SDSS Stripe~82. Note: this sub-sample includes all galaxies in the \texttt{stripe-82-single} sub-sample, with additional sources detected in the deeper imaging. (30,339 galaxies)

%ferengi <-- no table?
\item \texttt{redshifted}: Simulated \hst{} images constructed using SDSS images and artificially redshifted to between $0.3 \leq z \leq 1$. (288 original galaxies; 3,950 redshifted galaxies)

%\ref{tbl:simulated_agn}
\item \texttt{simulated-agn}: Simulated AGN host galaxies constructed using \hst{} images and PSFs. (96 original galaxies; 2,961 simulated AGN host galaxies)

@@

In order to test and correct for the effects of redshift, GZH includes a set of
calibration images. These images consist of the same galaxy as it would appear
over a variety of redshifts. The input images are from the SDSS
\citep{yor00,str02} and are processed to match the observational properties of 
the \hst{} surveys out to $z=1$. These
images were classified in the GZH interface using the same classification
scheme as the original \hst{} images. Further details on the creation of these images
is given in Section \ref{ssec:ferengi}.

@@

The GZH catalog is corrected for classification bias only for the first
question of the GZH decision tree (Section~\ref{sec:debiasing}), which asks
{\it ``Is the galaxy smooth and round, with no sign of a disk?''} For this
question, the catalog provides the additional parameters $\tt debiased$, $\tt
lower~limit$, $\tt upper~limit$, and $\tt best$ vote fractions. The $\tt best$
fraction for \ffeatures{} is chosen based on the categorization of the galaxy:
if it is ``correctable'', $\tt best = debiased$; if it is a lower limit, 
$\tt best = lower~limit$; if neither condition applies, then 
$\tt best = weighted$.

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for \hst{} images from AEGIS, COSMOS, GEMS, and GOODS\label{tbl:catalog_hst}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction$^{1}$} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ100002g  & 10010842  & AEGIS             & 0        & 127       & 0.118    & 0.128     & 0.085    & 0.085    & 0.226     & 0.226    \\
AHZ100002h  & 10010870  & AEGIS             & 4        & 127       & 0.567    & 0.592     & 0.927    & 0.592    & $-$       & $-$      \\
$\ldots$    \\
AHZ20004kd  & 20014731  & COSMOS            & 3        &  44       & 0.682    & 0.675     & 0.147    & 0.675    & $-$       & $-$      \\
AHZ20004ke  & 20014732  & COSMOS            & 2        &  45       & 0.689    & 0.756     & 0.893    & 0.756    & $-$       & $-$      \\
$\ldots$    \\
AHZ400043g  & 90022729  & GEMS              & 1        & 121       & 0.702    & 0.733     & 0.487    & 0.734    & 0.483     & 0.800    \\
AHZ4000416  & 90022735  & GEMS              & 1        & 127       & 0.646    & 0.698     & 0.508    & 0.698    & 0.171     & 0.727    \\
$\ldots$    \\
AGZ0007z47  & 10014     & GOODS-N-FULLDEPTH & 1        & 40        & 0.475    & 0.475     & 0.197    & 0.475    & 0.011     & 0.496    \\
AGZ0007z48  & 10017     & GOODS-N-FULLDEPTH & 3        & 40        & 0.675    & 0.675     & 0.048    & 0.675    & 0.168     & 0.669    \\
$\ldots$    \\
AGZ00083jb  & 8869      & GOODS-S-FULLDEPTH & 1        & 40        & 0.425    & 0.425     & 0.109    & 0.425    & 0.070     & 0.548    \\
AGZ00083jc  & 8878      & GOODS-S-FULLDEPTH & 0        & 40        & 0.205    & 0.205     & 0.048    & 0.048    & $-$0.005  & 0.287    \\
$\ldots$    \\
\enddata
\tablenotetext{1}{Flag indicating how the vote fractions for this galaxy were
corrected through debiasing (Section~\ref{ssec:zeta_results}), if possible.
0~=~correctable, 1~=~lower-limit ($f_{raw}$ --- $f_{adj}$ is not
single-valued), 2~=~uncorrected ($z_{\rm gal} < 0.3$), 3~=~uncorrected
(insufficient \ferengi{} galaxies in this $z$-$\mu$ bin), 4~=~uncorrected (no
galaxy redshift available).}
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 118,425~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

@@

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-faded Hubble images\label{tbl:catalog_faded}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZF000001  &   20000002    &   COSMOS  &   1   &   48 &  0.708   &     0.755   &   0.228    &    0.754 &   0.325   &   0.829  \\
AHZF000003  &   20000004    &   COSMOS  &   3   &   49 &  0.367   &     0.379   &   0.100    &    0.379 &   0.198   &   0.198  \\
AHZF000004  &   20000006    &   COSMOS  &   3   &   49 &  0.265   &     0.271   &   0.010    &    0.270 &   $-$	    &   $-$    \\
AHZF00000z  &   20000102    &   COSMOS  &   1   &   44 &  0.727   &     0.78    &   0.233    &    0.780 &   0.316   &   0.820  \\
AHZF000010  &   20000104    &   COSMOS  &   2   &   53 &  0.811   &     0.849   &   0.904    &    0.848 &   $-$	    &   $-$    \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for color-inverted Hubble images\label{tbl:catalog_recolored}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & & 
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZC000001	&   20000002	&   COSMOS	&   1	&   168	&   0.615   &   0.664   &   0.160   &  0.663   &  0.271    &  0.775    \\
AHZC000003	&   20000004	&   COSMOS	&   0	&   235	&   0.333   &   0.364   &   0.002   &  0.002   &  0.063    &  0.063    \\
AHZC000004	&   20000006	&   COSMOS	&   3	&   316	&   0.235   &   0.252   & $-0.011$  &  0.252   &  $-$	    &  $-$      \\
AHZC00000z	&   20000102	&   COSMOS	&   1	&   207	&   0.755   &   0.757   &   0.272   &  0.756   &  0.249    &  0.796    \\
AHZC000010	&   20000104	&   COSMOS	&   2	&   158	&   0.843   &   0.882   &   0.936   &  0.881   &  $-$	    &  $-$      \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 3,927~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}

\tabletypesize{\scriptsize}
\begin{deluxetable*}{lllcrllllll|c}
\centering
\tablecolumns{13}
\tablewidth{0pc}
\tablecaption{GZH morphological classifications for GOODS 2-epoch images\label{tbl:catalog_goods_shallow}} 
\tabletypesize{\scriptsize}
\tablehead{
 & & &  
\multicolumn{2}{c}{\underline{t01\_smooth\_or\_features\_}} &
\multicolumn{6}{c}{\underline{t01\_smooth\_or\_features\_a01\_smooth\_}} &
\colhead{$\ldots$}
\\
\colhead{Project ID} & 
\colhead{Hubble ID} & 
\colhead{Imaging} & 
\colhead{Correction} & 
\colhead{$N_\mathrm{votes}$} & 
\colhead{fraction} & 
\colhead{weighted} & 
\colhead{debiased} & 
\colhead{best} &
\colhead{lower~limit} & 
\colhead{upper~limit} &
\colhead{}
}
\small
\startdata
AHZ3000001  &   50000000    &     GOODS-N   &   0   &   123	&   0.390   &   0.415	&   0.090 &   0.090 &   $-$     &   $-$      \\
AHZ3000002  &   50000001    &     GOODS-N   &   2   &   126	&   0.341	&   0.355	&   0.356 &   0.356 &   0.220	&   0.279    \\
AHZ3000003  &   50000005    &     GOODS-N   &   1   &   129	&   0.760   &   0.826	&   0.633 &   0.825 &   0.596	&   0.834    \\
AHZ3000004  &   50000008    &     GOODS-N   &   1   &   120	&   0.758	&   0.787	&   0.639 &   0.787 &   0.658	&   0.834    \\
AHZ3000005  &   50000010    &     GOODS-N   &   1   &   123	&   0.854	&   0.890   &   0.611 &   0.889 &   0.597	&   0.914    \\
$\ldots$    \\
\enddata
\tablecomments{The full version of this table is available in electronic form,
as well as at \url{http://data.galaxyzoo.org}. The complete version includes
data for 6,144~galaxies and morphological information for all tasks in the
tree. A subset of the information is shown here to illustrate form and
content.}
\end{deluxetable*}
